Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-10-09 2016-Weak-FH-Bisim/WeakBisim.tex

\section{A model of process composition}
\label{sec:OT}

@@

\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec, and maybe one example on the Impl. OTs presented in latex readable form.}

@@

\subsection{Bisimulation for open pNets -- a Composable Bisimulation Theory}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open pNets:
\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is \True.
\end{definition}
We can now prove that pNet composition  preserves
FH-bisimulation. More precisely, one can define two preservation
properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
filled by the same pNet, in other words, composing a pNet with two
bisimilar contexts. The general case will be obtained by
transitivity of the bisimulation relation (Theorem~\ref{thm-equiv}).

>>>>

\section{A model of process composition}\label{sec:OT}
\TODO{Commenter la figure 2}

@@

\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec: Done, on the Counetr version !}

\TODO{:  and maybe one example on the Impl. OTs presented in latex readable form??}

\begin{figure}[t]
   \centerline{\includegraphics[width=9cm]{ATG/SPSpecOpen}}
   \caption{Specification OA (version with the error counter)}
   \label{SimpleProtCounter:SpecOA}
\end{figure}

@@

\subsection{Bisimulation for open pNets -- a Composable Bisimulation Theory}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open pNets:
\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is \True.
\end{definition}
\TODO{Predicate=True me pose un probleme... typiquement, on a besoin d'une ``condition initiale'', pour avoir des pNets data-oriented equivalents a leur version state-oriebted}

We can now prove that pNet composition  preserves
FH-bisimulation. More precisely, one can define two preservation
properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
filled by the same pNet, in other words, composing a pNet with two
bisimilar contexts. The general case will be obtained by
transitivity of the bisimulation relation (Theorem~\ref{thm-equiv}).
